No meaningful effects of COVID-19 related social media use on well-being

### 2021-11-30 analyses.RmD
- updated urls

Load packages, and make repo replicable.

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

# define packages
packages <- c("brms", "corrplot", "devtools", "GGally", "ggplot2", 
              "gridExtra", "haven", "kableExtra", "knitr", 
              "lavaan", "lme4", "magrittr", "mice", "mvnormalTest", "PerFit", 
              "psych", "quanteda.textstats",
              "pwr", "purrr", "semPlot", "semTools", "tidyverse")

# renv::install(packages)
# renv::install("tdienlin/td@v.0.0.2.5")  # uncomment to install
# renv::install("crsh/papaja@v0.1.0.9997")  # uncomment to install

>>>>

Load packages.

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

### 2021-11-30 analyses_additional.Rmd
- updated urls

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td")

# define packages
packages <- c("brms", "corrplot", "devtools", "GGally", "ggplot2", 
              "gridExtra", "haven", "kableExtra", "knitr", 
              "lavaan", "lme4", "magrittr", "mice", "mvnormalTest", "PerFit", 
              "psych", "quanteda.textstats",
              "pwr", "purrr", "semPlot", "semTools", "tidyverse")

# renv::install(packages)
# renv::install("tdienlin/td@v.0.0.2.5")  # uncomment to install
# renv::install("crsh/papaja@v0.1.0.9997")  # uncomment to install

>>>>

```{r r-setup, results='hide'}
# install packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")

# define packages
packages <- c("brms", "devtools", "GGally", "ggplot2", 
              "gridExtra", "kableExtra", "knitr", "lavaan", "lme4", 
              "magrittr", "mice", "mvnormalTest", 
              "PerFit", "psych", "quanteda.textstats", "semTools", "tidyverse")

### 2021-11-30 manuscript.Rmd
- updated urls

```{r analysis-preferences, include=F, cache=F}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
                      cache=T,
                      echo=F
                      # , fig.pos = 'h'
                      )
```

@@

# make project reproducible
# devtools::install_github("rstudio/renv")  # install renv
# renv::init()  # initialize renv

# install necessary packages
packages <- c("devtools", "english", "ggplot2", "kableExtra", 
              "lavaan", "lme4", "lmerTest",
              "magrittr", "semPlot", "tidyverse")
# renv::install(packages)
# renv::install("tdienlin/td@v.0.0.2.5")  # uncomment to install
# renv::install("crsh/papaja@v0.1.0.9997")  # uncomment to install
# renv::install("crsh/papaja@devel")  # uncomment to install

# load packages
lapply(c(packages, "papaja", "td"), library, character.only = TRUE)

# save snapshot of installed packages
# renv::snapshot()

# load workspace created from analyses.rmd to use results
load("data/workspace_2.RData")

# export references
# r_refs(file = "bibliography/r-references.bib")
```

During the COVID-19 pandemic, 
<!-- and especially in the beginning,  -->
numerous events unfolded in quick succession.
Several open questions emerged.
How dangerous is the virus? 
Is it spreading in my region? 
How is it transmitted, and how can I protect myself?
Because for many it was (and continues to be) a matter of life or death, people aimed to stay informed regarding the latest developments.
Governments around the world implemented safety measures, such as wearing masks, keeping physical distance, or enforcing lockdowns.
In this extraordinary situation, many people used media excessively to attain information, and especially social media were at an all time high [@statistaAverageDailyTime2021].

@@

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, p-value) I preregistered on the Open Science Framework. 
The (anonymous) preregistration can be accessed here: https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3.
Because in this study I analyzed data from an already existing large-scale data set, all of these steps were done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online [@kittelAustrianCoronaPanel2020].
In some cases I could not execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when inspecting the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online [companion website](https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html) (https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html).

@@

For more information on the analyses, for example a complete documentation of the models and their results, see [companion website](https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html).

@@

In what follows, I list all the variables that I analyzed.
For the variables' means, range, and variance, see Table \@ref(tab:descriptives).
For a complete list of all items and item characteristics, see [companion website](https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html).

@@

To find out whether my inferences were robust across legitimate alternative analyses, I reran the analyses also using standardized estimates,  mean scores instead of factor scores, and with a data set where missing data were not imputed.
The results were virtually the same.
For example, all standardized COVID-19 related types of social media use or channels were not significantly larger than a SESOI of $\beta$ = |.10|.
The additional analyses are reported in the [companion website](https://xmtra.github.io/Austrian_Corona_Panel_Project/analyses_additional.html).

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html).

>>>>

```{r analysis-preferences, include=F, cache=F}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed,
                      cache=T, echo=F
                      )
```

@@

# install necessary packages
# devtools::install_github("https://github.com/tdienlin/td@v.0.0.2.5")
# devtools::install_github("https://github.com/crsh/papaja@devel")

# load packages
packages <- c("devtools", "english", "ggplot2", "kableExtra", 
              "lavaan", "lme4", "lmerTest",
              "magrittr", "semPlot", "tidyverse")
lapply(c(packages, "papaja", "td"), library, character.only = TRUE)

# load workspace created from analyses.rmd to use results
load("data/workspace_2.RData")
```

During the COVID-19 pandemic, 
numerous events unfolded in quick succession.
Several open questions emerged.
How dangerous is the virus? 
Is it spreading in my region? 
How is it transmitted, and how can I protect myself?
Because for many it was (and continues to be) a matter of life or death, people aimed to stay informed regarding the latest developments.
Governments around the world implemented safety measures, such as wearing masks, keeping physical distance, or enforcing lockdowns.
In this extraordinary situation, many people used media excessively to attain information, and especially social media were at an all time high [@statistaAverageDailyTime2021].

@@

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, p-value) I preregistered on the Open Science Framework. 
The (anonymous) preregistration can be accessed here: https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3.
Because in this study I analyzed data from an already existing large-scale data set, all of these steps were done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online [@kittelAustrianCoronaPanel2020].
In some cases I could not execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when inspecting the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online [companion website](https://tdienlin.github.io/Austrian_Corona_Panel/index.html) (https://tdienlin.github.io/Austrian_Corona_Panel/index.html).

@@

For more information on the analyses, for example a complete documentation of the models and their results, see [companion website](https://tdienlin.github.io/Austrian_Corona_Panel/index.html).

@@

In what follows, I list all the variables that I analyzed.
For the variables' means, range, and variance, see Table \@ref(tab:descriptives).
For a complete list of all items and item characteristics, see [companion website](https://tdienlin.github.io/Austrian_Corona_Panel/index.html).

@@

To find out whether my inferences were robust across legitimate alternative analyses, I reran the analyses also using standardized estimates,  mean scores instead of factor scores, and with a data set where missing data were not imputed.
The results were virtually the same.
For example, all standardized COVID-19 related types of social media use or channels were not significantly larger than a SESOI of $\beta$ = |.10|.
The additional analyses are reported in the [companion website](https://tdienlin.github.io/Austrian_Corona_Panel/analyses_additional.html).

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (https://tdienlin.github.io/Austrian_Corona_Panel/index.html).

### 2021-11-30 manuscript.tex
- updated urls

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, p-value) I preregistered on the Open Science Framework.
The (anonymous) preregistration can be accessed here: \url{https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3}.
Because in this study I analyzed data from an already existing large-scale data set, all of these steps were done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online (Kittel et al., 2020).
In some cases I could not execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when inspecting the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online \href{https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html}{companion website} (\url{https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html}).

@@

For more information on the analyses, for example a complete documentation of the models and their results, see \href{https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html}{companion website}.

@@

In what follows, I list all the variables that I analyzed.
For the variables' means, range, and variance, see Table \ref{tab:descriptives}.
For a complete list of all items and item characteristics, see \href{https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html}{companion website}.

@@

To find out whether my inferences were robust across legitimate alternative analyses, I reran the analyses also using standardized estimates, mean scores instead of factor scores, and with a data set where missing data were not imputed.
The results were virtually the same.
For example, all standardized COVID-19 related types of social media use or channels were not significantly larger than a SESOI of \(\beta\) = \textbar.10\textbar.
The additional analyses are reported in the \href{https://xmtra.github.io/Austrian_Corona_Panel_Project/analyses_additional.html}{companion website}.

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (\url{https://xmtra.github.io/Austrian_Corona_Panel_Project/index.html}).

>>>>

The hypotheses, the sample, the measures, the analyses, and the inference criteria (SESOI, p-value) I preregistered on the Open Science Framework.
The (anonymous) preregistration can be accessed here: \url{https://osf.io/87b24/?view_only=b2289b6fec214fa88ee75a18d45c18f3}.
Because in this study I analyzed data from an already existing large-scale data set, all of these steps were done prior to accessing the data.
The preregistration was designed on the basis of the panel documentation online (Kittel et al., 2020).
In some cases I could not execute the analyses as I had originally planned, for example because some properties of the variables only became apparent when inspecting the actual data.
The most relevant deviations are reported below, and a complete list of all changes can be found in the online \href{https://tdienlin.github.io/Austrian_Corona_Panel/index.html}{companion website} (\url{https://tdienlin.github.io/Austrian_Corona_Panel/index.html}).

@@

For more information on the analyses, for example a complete documentation of the models and their results, see \href{https://tdienlin.github.io/Austrian_Corona_Panel/index.html}{companion website}.

@@

In what follows, I list all the variables that I analyzed.
For the variables' means, range, and variance, see Table \ref{tab:descriptives}.
For a complete list of all items and item characteristics, see \href{https://tdienlin.github.io/Austrian_Corona_Panel/index.html}{companion website}.

@@

To find out whether my inferences were robust across legitimate alternative analyses, I reran the analyses also using standardized estimates, mean scores instead of factor scores, and with a data set where missing data were not imputed.
The results were virtually the same.
For example, all standardized COVID-19 related types of social media use or channels were not significantly larger than a SESOI of \(\beta\) = \textbar.10\textbar.
The additional analyses are reported in the \href{https://tdienlin.github.io/Austrian_Corona_Panel/analyses_additional.html}{companion website}.

@@

All the stimuli, presentation materials, analysis scripts, and a reproducible version of the manuscript can be found on the companion website (\url{https://tdienlin.github.io/Austrian_Corona_Panel/index.html}).
